Towards Verifying the Bitcoin-S Library

### 2019-06-28 paper/paper.tex
work on project setup

In this chapter we look at the practical challenges that could occur
by using Stainless.  Since Stainless is still in development and there
is no 1.x release there might still be breaking changes and
improvements fixing problems described now.

\todo{nur über stainless-sbt-plugin reden damit man weiss wir haben es versucht}

\todo{
Kai:

sbt-plugin vs JAR:
Can use either sbt-plugin or JAR

@@

Reproduce results:
prereq: Java 8 in /usr/lib/jvm/java-8-openjdk
1. clone repo
2. run ./code/bin/stainless.sh <path to code>
   eg. ./code/bin/stainless.sh code/addition/src/main/scala/addition/reduced/
}

\subsection{stainless-sbt-plugin vs JAR}

@@

@@

Stainless requires and Scala recommends Java SE Development Kit 8.
Newer Java versions won't work.

@@

Now we can finally run Stainless on our code.  But this leads us to
the next findings.  We must rewrite most of the code, as described in
the previous chapters.

\begin{itemize}
\item clone our repo
\item jar vs sbt, you can use both
\item contains a stainless jar
\item call the script blahblah
\end{itemize}

>>>>

\paragraph{Using the Stainless-sbt-plugin vs Using the Stanless-JAR}

@@

@@

\paragraph{Reproducing our Results.}

Prerequisites:
\begin{enumerate}
\item Java 8 in /usr/lib/jvm/java-8-openjdk (Stainless requires and Scala recommends Java SE Development Kit 8. Newer Java versions won't work.)
\end{enumerate}

\begin{lstlisting}[language=bash]
 clone repo
 run ./code/bin/stainless.sh <path to code>
   eg. ./code/bin/stainless.sh code/addition/src/main/scala/addition/reduced/
\end{lstlisting}

@@

@@
